\documentclass[12pt,a4paper]{article}

% --> Declare packages / paths
\usepackage{graphicx}

\graphicspath{ {../imgs/} }

% --> Basic overlaying information
\title{Project \#1 - Standup Report \#1}
\author{Chris Nutter | Estrella Mejia | Kenneth Doan}

% --> Begin document information
\begin{document}

\maketitle
%\tableofcontents

%------------------------%
\section{Chris Nutter}
    1. Currently I'm working on getting the grid organized and properly formatted towards Professor Siska's recommendations.
    I have created the grid 41x41 and properly spaced out the grid itself. I have also hosted the P5 grid on my website 
    for our groupmates to look over live.
        \\\\
    2. Next I plan to fix a bug where mouse cursor mapping is off but that shouldn't be too hard.
        \\\\
    3. I'm still familiarizing with JS and P5 so adjusting to that is an annoying hurdle but it's helpful for 
    me to learn this for my own means. Professor Siska's comments on \emph{cs-sketches.js} help me 
    figure out what each thing does.   
%------------------------%

%------------------------%
\section{Estrella Mejia}
    1. I'm working on getting the ant to start at the center. 
        \\\\
    2. I plan to get the ant to move right on red or blue and left on black or green.
        \\\\
    3. I am trying to get the color properly 
%------------------------%
 
%------------------------%
\section{Kenneth Doan}
    1. I am trying to find the decimal color values for Black, Red, Yellow, Blue, and Green. 
    I am also trying to figure out how to turn the ant into a triangle in the meantime.
        \\\\
    2. Next I'll learn how to make the Ant start moving North at the start of the load.
        \\\\
    3. Implementing the triangle shape and the colours are some challenges 
    I am facing because this is the second class I have taken that is using HTML5.
%------------------------%
  
\end{document}
